Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
Typo

\begin{abstract}
%
Proving program termination is typically done by finding a well-founded
\emph{ranking function} for the program states.  Existing termination
provers typically find ranking functions using either linear algebra or
templates.  As such they are often restricted to finding linear ranking
functions over mathematical integers.  This class of ranking functions is
insufficient for prove termination for many terminating programs, and
furthermore a termination argument for a program operating on mathematical
integers does not always lead to a termination argument for the same program
operating on fixed-width machine integers.

>>>>

\begin{abstract}
%
Proving program termination is typically done by finding a well-founded
\emph{ranking function} for the program states.  Existing termination
provers typically find ranking functions using either linear algebra or
templates.  As such they are often restricted to finding linear ranking
functions over mathematical integers.  This class of ranking functions is
insufficient for proving termination of many terminating programs, and
furthermore a termination argument for a program operating on mathematical
integers does not always lead to a termination argument for the same program
operating on fixed-width machine integers.
